---
title: "ajd-sim-kbf"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ajd-sim-kbf}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Exact simulation of the Heston SV | SVJ | SVCJ models using the 
Kyriakou-Brignone-Fusai algorithm.

## Simulate returns of the Heston SV | SVJ | SVCJ models

```{r setup}
library(ajd.sim.kbf)
# Heston SV
v0 = 0.010201; k = 6.21; theta = 0.019; sigma = 0.61; rho = -0.7
r = 0.0319; tau = 1
N = 1000 # number of samples
Y = ryield_Hest(1000, v0, tau, r, k, theta, sigma, rho)
hist(Y, main="Heston SV model")
# SVJ
v0 = 0.008836; k = 3.99; theta = 0.014; sigma = 0.27; rho = -0.79
r = 0.0319; tau = 5; lambda = 0.11; mu_bar = -0.12; sigma_s = 0.15
N = 1000 # number of samples
Y = ryield_SVJ(N, v0, tau, r, k, theta, sigma, rho, 
               lambda, mu_bar, sigma_s)
hist(Y, main="SVJ model")
# SVCJ
v0 = 0.007569; k = 3.46; theta = 0.008; sigma = 0.14; rho = -0.82
r = 0.0319; tau = 1; lambda = 0.47; mu_bar = -0.1; sigma_s = 0.0001
mu_v = 0.05; rho_J = -0.38
N = 1000 # number of samples
Y = ryield_SVCJ(N, v0, tau, r, k, theta, sigma, rho, 
                lambda, mu_bar, sigma_s, mu_v, rho_J)
hist(Y, main="SVCJ model")
```

## Pricing the European call option Using Monte Carlo simulation

If your are interested in pricing the European call option using Monte Carlo
simulation for the Heston SV, SVJ and SVCJ models. Please refer to functions
`?price_Hest`, `?price_SVJ` and `?price_SVCJ`.

## References

- Kyriakou, I., Brignone, R., & Fusai, G. (2024). Unified moment-based modeling
of integrated stochastic processes. *Operations Research*, 72(4), 1630-1653.

- Broadie, M., & Kaya, Ö. (2006). Exact simulation of stochastic volatility and
other affine jump diffusion processes. *Operations Research*, 54(2), 217-231.
